### 2016-10-07 revision/lower-bound.tex
minor fix

The upper bound on regret of \textsc{SOLO FTRL} is of
the form $O(\sqrt{\sup_{v \in K} f(v) \sum_{t=1}^T \|\ell_t\|_*^2})$ where $f$
is any $1$-strongly convex function with respect to $\|\cdot\|$.  The same
upper bound is also achieved by \textsc{FTRL} with a constant learning rate
when the number of rounds $T$ and $\sum_{t=1}^T \|\ell_t\|_*^2$ are known
upfront \cite[Chapter 2]{Shalev-Shwartz-2011}.  The lower bound is
$\Omega(D\sqrt{\sum_{t=1}^T \|\ell_t\|_*^2})$.

>>>>

The upper bound on regret of \textsc{SOLO FTRL} is of
the form $O(\sqrt{\sup_{v \in K} f(v) \sum_{t=1}^T \|\ell_t\|_*^2})$ where $f$
is any $1$-strongly convex function with respect to $\|\cdot\|$.  The same
upper bound is also achieved by \textsc{FTRL} with a constant learning rate
when $\sum_{t=1}^T \|\ell_t\|_*^2$ is known
upfront \cite[Chapter 2]{Shalev-Shwartz-2011}.  The lower bound is
$\Omega(D\sqrt{\sum_{t=1}^T \|\ell_t\|_*^2})$.
